Infinite diameter confidence sets in a model for publication bias

### 2020-04-24 infiniteci.tex
:pear: Fixed title.
:fish: Changed layout.

\documentclass{article}

\usepackage{arxiv}
\usepackage{natbib}
\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage[colorlinks=true, citecolor = blue]{hyperref}      % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{graphicx, subfigure}
\usepackage{lipsum}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{import}
\usepackage{enumitem}
\usepackage{csquotes}
\usepackage{todonotes}
\usepackage{xfrac}

%%% ============================================================================
%%% Theorems.
%%% ============================================================================
\theoremstyle{plain}
\newtheorem{thm}{\protect\theoremname}
\theoremstyle{plain}
\newtheorem{lem}{\protect\lemmaname}
\theoremstyle{definition}
\newtheorem{defn}[thm]{\protect\definitionname}
\theoremstyle{remark}
\newtheorem{rem}[thm]{\protect\remarkname}
\theoremstyle{definition}
\newtheorem{example}[thm]{\protect\examplename}
\theoremstyle{plain}
\newtheorem{cor}[thm]{\protect\corollaryname}
\theoremstyle{plain}
\newtheorem{prop}[thm]{\protect\propositionname}
\theoremstyle{definition}
\newtheorem{xca}[thm]{\protect\exercisename}
\ifx\proof\undefined
\newenvironment{proof}[1][\protect\proofname]{\par
	\normalfont\topsep6\p@\@plus6\p@\relax
	\trivlist
	\itemindent\parindent
	\item[\hskip\labelsep\scshape #1]\ignorespaces
}{%
	\endtrivlist\@endpefalse
}
\providecommand{\proofname}{Proof}
\fi

\providecommand{\corollaryname}{Corollary}
\providecommand{\definitionname}{Definition}
\providecommand{\propositionname}{Proposition}
\providecommand{\examplename}{Example}
\providecommand{\exercisename}{Exercise}
\providecommand{\remarkname}{Remark}
\providecommand{\theoremname}{Theorem}
\providecommand{\lemmaname}{Lemma}

@@

\title{Please avoid the standardized alpha}

\author{
  Jonas Moss \\
  Department of Mathematics, University of Oslo\\
  PB 1053, Blindern, NO-0316, Oslo, Norway \\
  \it{jonasmgj@math.uio.no}
}

@@

The problem with non-existence
of confidence sets with guaranteed finite diameter for finite-dimensional
parameters has not received much attention in the statistical literature,
as lamented by \citet{gleser996bootstrap}. Some references in this
area are \citet{bahadur1956nonexistence}, who studied infinitely
large confidence sets in non-parametric estimation of the mean, \citeauthor{romano2004non}'s
(2004) extension of their results, \citet{Donoho1988-hg} and \citet{Pfanzagl1998-fe}.
\begin{lem}
Let $C$ be a confidence set and $A_{g(\theta)}$ its associated
acceptance sets. If there exists a sequence $\left\{ \theta_{n}\right\} _{n=1}^{\infty}$
with $\left\Vert g(\theta_{n})\right\Vert \to\infty$ such
that $\lim_{n\to\infty}P_{\theta}(A_{g(\theta_{n})})>0,$then
the diameter of $C$ at $\theta$ is infinite with positive probability.
\end{lem}
\begin{proof}
Assume without loss of generality that $\left\Vert g(\theta_{n})\right\Vert \geq n$
for each $n$; such a sequence can always be found by appropriately
filtering the original $\left\{ \theta_{n}\right\} _{n=1}^{\infty}$.
Since $\left\{ D\geq n\right\} $ is a decreasing sequence of sets,
$P_{\theta}(D=\infty)=\lim_{n\to\infty}P_{\theta}(D\geq n)$
for each $\theta$. From $A_{g(\theta_{n})}\subseteq\left\{ D\geq n\right\} $
it follows that $P_{\theta}(A_{g(\theta_{n})})\leq P_{\theta}(D\geq n)$,
thus $P_{\theta}(D=\infty)=\lim_{n\to\infty}P_{\theta}(D\geq n)\geq\lim_{n\to\infty}P_{\theta}(A_{g(\theta_{n})})>0$.
\end{proof}
This is the extension of the Gleser-Hwang theorem.
\begin{thm}
\label{thm:Infinite diameter main theorem}If there exists a sequence
$\left\{ \theta_{i}\right\} _{i\in\mathbb{N}}$ with $\left\Vert g(\theta_{i})\right\Vert \to\infty$
such that $p_{\theta_{i}}\to f^{\star}$ pointwise and $\textrm{supp}p_{\theta}=\textrm{supp}f^{\star}$
for each $\theta$, then every confidence set with coverage $1-\alpha>0$
has infinite diameter with positive probability.
\end{thm}
\begin{proof}
Assume without loss of generality that $\left\Vert g(\theta_{n})\right\Vert \geq n$.
By a variant of the dominated convergence theorem \citep[exercise 16.4a]{billingsley1995probability},$\int_{D\geq n}p_{\theta_{n}}d\mu\to\int_{D=\infty}f^{\star}d\mu$.
Since $A_{g(\theta_{n})}\subseteq\left\{ D\leq n\right\} $,
$1-\alpha\leq\int_{A_{g(\theta_{n})}}p_{\theta_{n}}d\mu\leq\int_{D\geq n}p_{\theta_{n}}d\mu$
for all $n$, thus $\int_{D=\infty}f^{\star}d\mu>1-\alpha>0$. The
result follows from $P_{\theta}(D\geq n)=\int_{D\geq n}(p_{\theta}/p_{\theta_{n}})p_{\theta_{n}}d\mu>\int_{D=\infty}(p_{\theta}/f^{\star})f^{\star}d\mu>0$.
\end{proof}
This an extension of Theorem \ref{thm:Infinite diameter main theorem}
to mixture distributions.
\begin{prop}
\label{cor:Mixture model corollary}Let $f_{\theta}^{1},f_{\theta}^{2},\ldots$
be a finite or infinite sequence of densities, $\pi(\theta)$
a countable probability vector and $\sum_{n=1}^{\infty}\pi_{n}(\theta)f_{\theta}^{n}$
a mixture distribution. Assume there is a sequence $\left\{ \theta_{i}\right\} _{i\in\mathbb{N}}$
with $\left\Vert g(\theta_{i})\right\Vert \to\infty$ such
that $f_{\theta_{i}}^{1}\to f^{\star}$ pointwise and $\textrm{supp}f_{\theta}^{1} = \textrm{supp}f^{\star}$
for each $\theta$ . If there is a parameter $\theta'\in\Theta$ satisfying
$\pi_{1}(\theta')>\alpha$, the mixture $\sum_{n=1}^{\infty}\pi_{n}(\theta)f_{\theta}^{n}$
admits no almost surely finite diameter confidence set of coverage
$1-\alpha$ for $g(\theta)$.
\end{prop}

@@

\bibliographystyle{apalike}
\bibliography{infiniteci}
\end{document}

>>>>

\documentclass[twoside]{article}
\usepackage{arxiv}
% \usepackage{natbib}
% \usepackage[utf8]{inputenc} % allow utf-8 input
% \usepackage[T1]{fontenc}    % use 8-bit T1 fonts
% \usepackage[colorlinks=true, citecolor = blue]{hyperref}      % hyperlinks
% \usepackage{url}            % simple URL typesetting
% \usepackage{booktabs}       % professional-quality tables
% \usepackage{amsfonts}       % blackboard math symbols
% \usepackage{nicefrac}       % compact symbols for 1/2, etc.
% \usepackage{microtype}      % microtypography
% \usepackage{graphicx, subfigure}
% \usepackage{lipsum}
% \usepackage{amsmath}
% \usepackage{amsthm}
% \usepackage{amssymb}
% \usepackage{import}
% \usepackage{enumitem}
% \usepackage{csquotes}
% \usepackage{todonotes}
% \usepackage{xfrac}

@@

\title{Infinite diameter confidence sets in a model for publication bias}

\author{
  Jonas Moss \orcid{0000-0002-6876-6964} \\
  Department of Mathematics, University of Oslo\\
  PB 1053, Blindern, NO-0316, Oslo, Norway \\
  \it{jonasmgj@math.uio.no}
}

\titletag{An arXiv preprint, v1.1}
\makeatletter
\titlerunning{\@title}
\makeatother
\authorrunning{Jonas Moss}

@@

The problem with non-existence
of confidence sets with guaranteed finite diameter for finite-dimensional
parameters has not received much attention in the statistical literature,
as lamented by \citet{gleser996bootstrap}. Some references in this
area are \citet{bahadur1956nonexistence}, who studied infinitely
large confidence sets in non-parametric estimation of the mean, \citeauthor{romano2004non}'s
(2004) extension of their results, \citet{Donoho1988-hg} and \citet{Pfanzagl1998-fe}.
\begin{lem}
Let $C$ be a confidence set and $A_{g(\theta)}$ its associated
acceptance sets. If there exists a sequence $\left\{ \theta_{n}\right\} _{n=1}^{\infty}$
with $\left\Vert g(\theta_{n})\right\Vert \to\infty$ such
that $\lim_{n\to\infty}P_{\theta}(A_{g(\theta_{n})})>0,$then
the diameter of $C$ at $\theta$ is infinite with positive probability.
\end{lem}
\begin{proof}
Assume without loss of generality that $\left\Vert g(\theta_{n})\right\Vert \geq n$
for each $n$; such a sequence can always be found by appropriately
filtering the original $\left\{ \theta_{n}\right\} _{n=1}^{\infty}$.
Since $\left\{ D\geq n\right\} $ is a decreasing sequence of sets,
$P_{\theta}(D=\infty)=\lim_{n\to\infty}P_{\theta}(D\geq n)$
for each $\theta$. From $A_{g(\theta_{n})}\subseteq\left\{ D\geq n\right\} $
it follows that $P_{\theta}(A_{g(\theta_{n})})\leq P_{\theta}(D\geq n)$,
thus $P_{\theta}(D=\infty)=\lim_{n\to\infty}P_{\theta}(D\geq n)\geq\lim_{n\to\infty}P_{\theta}(A_{g(\theta_{n})})>0$.
\end{proof}
This is the extension of the Gleser-Hwang theorem.
\begin{thm}
\label{thm:Infinite diameter main theorem}If there exists a sequence
$\left\{ \theta_{i}\right\} _{i\in\mathbb{N}}$ with $\left\Vert g(\theta_{i})\right\Vert \to\infty$
such that $p_{\theta_{i}}\to f^{\star}$ pointwise and $\textrm{supp}p_{\theta}=\textrm{supp}f^{\star}$
for each $\theta$, then every confidence set with coverage $1-\alpha>0$
has infinite diameter with positive probability.
\end{thm}
\begin{proof}
Assume without loss of generality that $\left\Vert g(\theta_{n})\right\Vert \geq n$.
By a variant of the dominated convergence theorem \citep[exercise 16.4a]{billingsley1995probability}, $\int_{D\geq n}p_{\theta_{n}}d\mu\to\int_{D=\infty}f^{\star}d\mu$.
Since $A_{g(\theta_{n})}\subseteq\left\{ D\leq n\right\} $,
$1-\alpha\leq\int_{A_{g(\theta_{n})}}p_{\theta_{n}}d\mu\leq\int_{D\geq n}p_{\theta_{n}}d\mu$
for all $n$, thus $\int_{D=\infty}f^{\star}d\mu>1-\alpha>0$. The
result follows from $P_{\theta}(D\geq n)=\int_{D\geq n}(p_{\theta}/p_{\theta_{n}})p_{\theta_{n}}d\mu>\int_{D=\infty}(p_{\theta}/f^{\star})f^{\star}d\mu>0$.
\end{proof}
This an extension of Theorem \ref{thm:Infinite diameter main theorem}
to mixture distributions.
\begin{prop}
\label{cor:Mixture model corollary}Let $f_{\theta}^{1},f_{\theta}^{2},\ldots$
be a finite or infinite sequence of densities, $\pi(\theta)$
a countable probability vector and $\sum_{n=1}^{\infty}\pi_{n}(\theta)f_{\theta}^{n}$
a mixture distribution. Assume there is a sequence $\left\{ \theta_{i}\right\} _{i\in\mathbb{N}}$
with $\left\Vert g(\theta_{i})\right\Vert \to\infty$ such
that $f_{\theta_{i}}^{1}\to f^{\star}$ pointwise and $\textrm{supp}f_{\theta}^{1} = \textrm{supp}f^{\star}$
for each $\theta$ . If there is a parameter $\theta'\in\Theta$ satisfying
$\pi_{1}(\theta')>\alpha$, the mixture $\sum_{n=1}^{\infty}\pi_{n}(\theta)f_{\theta}^{n}$
admits no almost surely finite diameter confidence set of coverage
$1-\alpha$ for $g(\theta)$.
\end{prop}

@@

\bibliography{infiniteci}
\end{document}
